Case study of Scalable Quantum Simulation of Molecular Energies

### 2019-06-21 article.tex
general updates5

\section{Non-technical background}

@@

\section{Techniques in paper}
If I asked you how to make a cup of coffee, your response would go a little something like this; prepare a cup (clean of course), put a number of
 teaspoons of coffee (depends on how strong you like your coffee), boil the kettle, pour the hot water into the cup and lastly stir. You have now
 made your cup of instant coffee by following a set of instructions.

@@

\subsection{The Experimental Implementation}

@@

\section{Conclusion and outlook}

@@

>>>>

\section{Scientific Background}

@@

\section{Techniques in Paper}
If I asked you how to make a cup of coffee, your response would go a little something like this; prepare a cup (clean of course), put a number of
 teaspoons of coffee (depends on how strong you like your coffee), boil the kettle, pour the hot water into the cup and lastly stir. You have now
 made your cup of instant coffee by following a set of instructions.

@@

\subsection{Experimental Implementation}

@@

\section{Conclusion and Outlook}

@@

\section{Afterword}

Shuhao Yang wrote the Introduction and History sections and the PEA section and box. James Mills wrote the Scientific Background and Conclusion
and Outlook sections and the Experimental Implementation section and box. Shanice St John wrote the Techniques in Paper section introduction and
the Main Achievement of Paper section, and the VQE section and box. However we all edited and redrafted together and interviewed the academics
whose opinions we quoted in the article. We would like to thank Dr Abolfazl Bayat, Prof. Dan Browne and Mikolaj Uryszek for kindly talking to
us and allowing us to quote them here.
